Location of interaction vertices is 
%an important ingredient to precision particle-physics measurements. It is 
important in order to know which particles are
associated with the primary interaction vertex, and to construct parameters such as the
longitudinal and transverse impact parameters, which can be used to distinguish 
%signal leptons from fakes, 
leptons from conversions or from secondary decays in jets.
In the ATLAS reconstruction process vertex-finding occurs after reconstruction of
\id\ tracks, as described in \sec{reco-tracking}. The
vertex-finding algorithm must associate tracks with primary vertices, and obtain
a best fit for the vertex position and its uncertainty. 
%Two approaches are used in ATLAS for associating tracks with vertices. 

%In `finding-after-fitting',
%tracks are preselected by requiring that they are consistent with the collision
%region. The tracks are ordered by their longitudinal impact parameter, and a
%sliding window algorithm is used to identify clusters of tracks. A fit is 
%carried out to obtain the vertex position. Outlier tracks are then removed if
%they have a \chisquared\ with a probability of being consistent with the vertex
%of less than 8\%. The vertex is then refitted, and the process iterates until
%there are no outliers left, or the cluster becomes too small. In this procedure
%the maximum number of vertices produced is determined at the clustering stage, and
%once discarded, outlier tracks are not used again. This can be sub-optimal in
%busy environments if the initial seeding does not correctly identify clusters.
%
%An alternative approach, with better handling of outliers, is
%`finding-through-fitting'~\cite{1742-6596-119-3-032033}. This is the default approach in ATLAS. Tracks are
%again preselected by consistency with the interaction region, but in this case a
%single seed vertex is formed out of all the preselected tracks. This is fitted, and
%tracks identified as outliers in the fit are used to create a second vertex
%seed. A simultaneous fit is then carried out of the two vertices, and again
%outlier tracks are used to create a new primary vertex. The procedure is
%iterated until none of the remaining outliers fits with any vertex with a
%\chisquared\ probability of more than 1\%.

%An `Adaptive Vertex Finding'~\cite{0954-3899-34-12-N01} algorithm is used in
%both cases for the vertex position fitting. 
%This uses a Kalman filter to minimise the least squares distances of the tracks from
%the vertex position. After a preliminary fit, tracks are assigned a
%weight depending on their compatibility with the vertex, with outlier tracks
%being down-weighted so as to have less of a pull on the vertex position. The
%process is iterated until convergence.

The default ATLAS approach to vertex finding is called
`finding-through-fitting' \cite{1742-6596-119-3-032033}. Tracks are preselected
by consistency with the interaction region, and a single seed vertex is formed
out of all the preselected tracks. This is fitted using an `Adaptive Vertex
Finding'~\cite{0954-3899-34-12-N01} algorithm, which uses a Kalman filter to
minimise the least squares distances of the tracks from the vertex position.
After a preliminary fit, tracks are assigned a weight depending on their
compatibility with the vertex, with outlier tracks being down-weighted so as to
have less of a pull on the vertex position. The process is iterated until
convergence.  Following the fit, tracks identified as outliers are used to
create a second vertex seed. A simultaneous fit is then carried out of the two
vertices, and again outlier tracks are used to create a new primary vertex. The
procedure is iterated until none of the remaining outliers fits with any vertex
with a \chisquared\ probability of more than 1\%.
