\chapter*{Acknowledgements}
I would like acknowledge and thank the Science and Technology Facilities Council
(STFC) for their financial support over the last three and a half years,
including support for a fantastic two years spent on Long Term Attachment at CERN
in Geneva.

Many thanks to my supervisor Aidan Robson for expert guidance and support throughout my
PhD, particularly for pointing me onto the path of \ZZ\ measurements in the first
place, which I believe was a very rewarding decision, even if Aidan's original
motivation for encouraging me to study \ZZ\ decays unfortunately didn't come to
pass! And of course also for reading drafts of this thesis. Thanks also to Tony
Doyle for acting as my second supervisor.
%members of the Glasgow PPE group: Tony Doyle for acting as my second supervisor,
%Andrew Pickford for putting up with me doing my best to bring down the Glasgow
%batch system, James Ferrando
I would like to thank the other (current and former) Glasgow PhD students who put up with me and
helped keep me sane: big Mike, Donny, Will, Paul, ginger Mike, Cristina,
Alistair, and the everyone else in the Glasgow PPE group for making it a very
friendly environment to work in.

For my work on the SCT temperature monitoring I thank Saverio D'Auria
for helping me get started, for exhaustive knowledge of all things SCT, and for
letting me share his office for two years. Thank you also to Steve McMahon for
discussion of results.

% ZZ people
I am indebted to Shih-Chieh Hsu, for very enthusiastic
support, guidance and constructive criticism in my initial work on \ZZ, and
also for having the confidence in me to appoint me as analysis contact for the
preliminary 8~\tev\ measurement. I would also like to thank Kostas Kordas,
Andrew Nelson, Advait Nagarkar, Joshua Moss, and the rest of the \ZZ\ analysis
group, who were all wonderful people to work with, even after multiple sleepless
nights! Thank you to Vasiliki Kouskoura for helping me get started with the
\TGC\ limit setting, and to Will Buttinger for many discussions regarding the
limit setting procedure (amongst many other things \ZZ\ related).
% Potential other ZZ people: Pat, Hayes, Laillin, Daniel Whiteson, Andreas,
% Sofia, Other SM people: JB, Joao, 

% Other students
Thank
